Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-11-21 latex/paper.tex
添加各向异性随长度的变化

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-20 20:47:21
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Before calculating thermal transportation properties , the  structures are  optimized with  conjugate gradient (CG) method which guarantee the stability of them .  Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract second- and third-order force constants (FCs) in which hundreds of  slightly displaced supercells are generated and their forces are calculated with LAMMPS and used to calculate the FCs with  numerical differential calculation. The chosen supercells is $3 \times 3 \times 1$ of premitive cells to make the inplane dimension above  $40\angstrom$ which make  forces acurrate enough. As for the out-of-plane dimension, according to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

With the increase of layer number the anisotropy decreases for layer number larger than three. Here we study mainly on multilayer silicene structure with 3-8 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction.   From TABLE.\ref{tab:table1}, for the stuctures with more than three layers,the thermal conductivity of the multilayer silicene with zigzag type is higher than that of armchair. $\kappa_z$ decreases while $\kappa_a$ increases. The reason is that the zigzag direction of the multilayer silicene surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}). Compared with the bulk silicene structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow. While along the armchair direction, the fluctuation of multilayer silicene surface is very large, the same is its obvious affection on heat flow. This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicene. It's expected that when the layer number reaches infinity the value of them collapse because we finally obtain the bulk phase. The value $ \chi=|\kappa_{z,\infty}-\kappa_{a,\infty} |/max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) \times 100 \%$ is used to measure the thermal conductivity difference in different directions, where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction. And is $ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) $ the maximum value of thermal conductivity in the two directions. The magnitude of the anisotropy $\chi$ is also shown in TABLE.\ref{tab:table1},which  decreases obviously for these structures which is expected. The case of three layers is exceptional whose values are much larger than the structures with those with larger layer number and possesses a smaller anisotropy. This could be understood by the direct interaction beteen the top and bottom sides , and also the absence of hexatomic ring in the side view compared with 4l1 structure.A deeper analysis of this of it could be found in work of Guo \cite{Guo2015Structural}.

On the other hand, the size effect of the thermal conductivity anisotropy is obvious. As shown in FIG.\ref{fig:tc_length_sheng}(b), at the same thickness, in the case of shorter length (10 - 50nm), the anisotropy is obvious. When the length is about 100nm, the anisotropy difference becomes very small. This is essentially due to the difference in the out-of-plane acoustic branch (LA), the transverse acoustic branch (TA), and the vertical plane acoustic phonon (ZA) of the multilayer silicene structures along different directions. However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.

@@

To obtain a clear connection between  the surface characteristic we also statistic the force constants of different position of the structures.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-20 22:20:51
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Before calculating thermal transportation properties, the  structures are  optimized with  conjugate gradient (CG) method which guarantee the stability of them .  Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract second- and third-order force constants (FCs) in which hundreds of  slightly displaced supercells are generated and their forces are calculated with LAMMPS and used to calculate the FCs with  numerical differential calculation. The chosen supercells is $3 \times 3 \times 1$ of premitive cells to make the inplane dimension above  $40\angstrom$ which make  forces acurrate enough. As for the out-of-plane dimension, according to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/chi}{}
  \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
\end{figure}

With the increase of layer number the anisotropy decreases for layer number larger than three. Here we study mainly on multilayer silicene structure with 3-8 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction.   From TABLE.\ref{tab:table1}, for the stuctures with more than three layers,the thermal conductivity of the multilayer silicene with zigzag type is higher than that of armchair. $\kappa_z$ decreases while $\kappa_a$ increases. The reason is that the zigzag direction of the multilayer silicene surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}). Compared with the bulk silicene structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow. While along the armchair direction, the fluctuation of multilayer silicene surface is very large, the same is its obvious affection on heat flow. This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicene. It's expected that when the layer number reaches infinity the value of them collapse because we finally obtain the bulk phase. The value
\begin{equation}
  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
\end{equation}

is used to measure the thermal conductivity difference in different directions, where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction. And is $ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) $ the maximum value of thermal conductivity in the two directions. The magnitude of the anisotropy $\chi$ is also shown in TABLE.\ref{tab:table1},which  decreases obviously for these structures which is expected. The case of three layers is exceptional whose values are much larger than the structures with those with larger layer number and possesses a smaller anisotropy. This could be understood by the direct interaction beteen the top and bottom sides , and also the absence of hexatomic ring in the side view compared with 4l1 structure.A deeper analysis of this of it could be found in work of Guo \cite{Guo2015Structural}.

On the other hand, the size effect of the thermal conductivity anisotropy is obvious in 2l1 but not in the others. As shown in FIG.\ref{fig:chi}, thermal conductivity in 2l1 is almost isotropic  in the case of short length (10 - 1000 $\angstrom$). When the length is above 1000  $\angstrom$), thermal conductivity become inceasingly anisotropic. This is essentially due to the difference acoustic branch along different directions whose mean free path are rather large, which is caused by phonon scattering of umklapp process. However, for 3-8 layer structures, thermal conductivity is highly even in the short free path region which indicates anistropy in both low and high frequency range and this could  be verified in the following contents. The anisotropy in 2lhex is somelike the mixture of both mechanism but has also a pretty large contribution from long path phonons.

@@
